\documentclass[a4paper,10pt]{article}

% ---------------- Packages ----------------
\usepackage[margin=1.1cm]{geometry}
\usepackage{fontspec}
\setmainfont{Arial}
\setsansfont{Arial}
\setmonofont{Courier New}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{tikz}

% ---------------- Colors ----------------
\definecolor{primary}{HTML}{0F172A}   % Dark slate
\definecolor{accent}{HTML}{2563EB}    % Executive blue
\definecolor{muted}{HTML}{64748B}     % Muted gray

% ---------------- Section Style ----------------
\titleformat{\section}
  {\large\bfseries\sffamily\color{primary}}
  {}{0em}{}
  [\vspace{-0.2em}\titlerule]

% ---------------- Custom Commands ----------------
\newcommand{\role}[4]{%
\textbf{#1} \hfill {\color{muted}#2}\\%
\textit{#3} \hfill {\color{muted}#4}%
}

\newcommand{\metric}[1]{\textbf{\color{accent}#1}}

% ---------------- Document ----------------
\begin{document}

% ---------------- Header ----------------
\begin{center}
    {\LARGE \textbf{Dr. Suraj Nair}}\\
    \vspace{2mm}
    \textit{Founder \& CEO \quad \textbar \quad PhD in AI and Robotics \quad \textbar \quad Scaling Deep-Tech to Global Enterprise}\\
    \vspace{2mm}
    \faMapMarker\ Singapore \quad
    \faPhone\ +65 8506 0679 \quad
    \faFlag\ Singaporean \quad
    \faEnvelope\ \href{mailto:surajnair1@gmail.com}{surajnair1@gmail.com} \\
    \vspace{1mm}
    \faLinkedin\ \href{https://linkedin.com/in/dr-suraj-nair-3663617}{LinkedIn} \quad
    \faGlobe\ \href{https://speedcargo.sg}{Company Website} \quad
    \faGraduationCap\ \href{https://scholar.google.com/citations?user=zM-qft4AAAAJ&hl=en}{Google Scholar}
\end{center}

\vspace{4mm}

% ---------------- Executive Summary ----------------
\section*{EXECUTIVE SUMMARY}
\textbf{Founder and CEO with 15+ years of experience in AI, robotics, and computer vision}, scaling deep-tech innovations into enterprise-grade products. Experienced in \textbf{startup leadership, fundraising, enterprise sales, and C-level engagement}, with global deployments across Asia, Europe, and the Middle East. PhD in Artificial Intelligence and Robotics (Technical University of Munich, Germany).

% ---------------- Key Highlights ----------------
\section*{KEY HIGHLIGHTS}
\begin{itemize}[leftmargin=*, label=-]
    \item \textbf{Founded and scaled} Speedcargo Technologies to \metric{US\$700K ARR}, deploying AI solutions across 15+ countries.  
    \item Raised \metric{US\$4.5M} in startup funding and S\$41M government grants (for research institutes across multiple programs).  
    \item Established \textbf{C-level engagements and commercial contracts} with global airlines and ground handlers. 
    \item \textbf{Built and led cross-functional teams} in AI, robotics and mission critical software intensive systems; established C-level partnerships; keynote speaker at IATA, STAT Media, GHI, Emirates Group.  
    \item Winner, Startup World Cup Singapore Chapter; \textbf{regular speaker} at flagship events in Air Cargo and beyond
\end{itemize}

% ---------------- Experience ----------------
\section*{EXPERIENCE}
\role{Founder \& Chief Executive Officer}{2020 -- Present}{\href{https://speedcargo.sg}{\textcolor{primary}{Speedcargo Technologies}}, Singapore}{}
\begin{itemize}[leftmargin=*, label=-]
    \item Founded and scaled an AI and robotics startup, raising \metric{US\$4.5M} and growing revenue to \metric{US\$700K} ARR through multi-million-dollar enterprise contracts. To grow to \metric{US\$2M} ARR in 2026.
    \item Built and led cross-functional teams across strategy, product, sales, and board governance, deploying AI-powered solutions globally (Asia, Europe, Middle East, Australia) for Tier-1 global airlines and ground handlers in Air Cargo
    \item Established strategic partnerships with \textbf{Microsoft Corporation and Güdel AG}; regular keynote speaker at global aviation and logistics events.
\end{itemize}

\role{Principal}{2026 -- Present}{\href{https://www.epiphyte.io/}{Epiphyte}, Singapore}{}
\begin{itemize}[leftmargin=*, label=-]
    \item Leads strategy, business development, and AI/Robotics initiatives, contributing to product and software development.
\end{itemize}

\role{Principal Investigator \& Program Lead}{2014 -- 2020}{\href{https://www.tum-create.edu.sg/}{TUMCREATE}, Singapore}{}
\begin{itemize}[leftmargin=*, label=-]
    \item Led the SPEEDCARGO robotics program, later commercialized as Speedcargo Technologies, building and directing multidisciplinary AI, robotics, and simulation teams.  
    \item Part of the leadership team securing and managing USD 40M+ in competitive research and industry funding.  
    \item Delivered joint projects with SATS, A*STAR, Continental AG, and global partners; collaborated with government agencies and C-level stakeholders, reporting directly to the CEO.
\end{itemize}

\role{Research Fellow \& Project Leader – AI \& Robotics}{2012 -- 2014}{\href{https://www.fortiss.org/}{fortiss GmbH}, Germany}{}
\begin{itemize}[leftmargin=*, label=-]
    \item Led the EU FP7 flagship project SMErobotics, driving industrial robotics, AI systems, and human–robot interaction.  
    \item Collaborated with KUKA, COMAU, Güdel, DLR, Fraunhofer, and other European partners to deliver scalable automation solutions for manufacturing and industrial environments.
\end{itemize}

\role{Research Associate – AI \& Robotics}{2007 -- 2011}{\href{https://www.tum.de/}{Technical University of Munich}, Germany}{}
\begin{itemize}[leftmargin=*, label=-]
    \item PhD research in AI, computer vision, and robotics for industrial systems.
    \item Collaborated with BMW, Audi, Siemens, KUKA, ABB, and Bosch.  
    \item Research Fellow on DFG-funded OR.NET project (medical systems interoperability).  
    \item Developed robust AI and vision systems deployed in industrial environments.
\end{itemize}

\role{Research Assistant – Computer Vision}{2006 -- 2007}{\href{https://www.philips.com/a-w/about/research.html}{Philips Research Laboratories}, The Netherlands}{}
\begin{itemize}[leftmargin=*, label=-]
    \item Conducted research on computer vision and gaze-tracking systems within multidisciplinary research teams at Philips Research.
\end{itemize}

\role{GPRS Engineer – Mobile Telecommunications Systems}{2005}{\href{https://www.orange.com/}{Orange} (now \href{https://www.vodafone.com/}{Vodafone}), India}{}
\begin{itemize}[leftmargin=*, label=-]
    \item Supported large-scale telecom back-end systems (SMS, MMS, billing) and collaborated with global vendors including Ericsson, Motorola, and Nokia.
\end{itemize}

% ---------------- Board & Advisory ----------------
\section*{BOARD \& ADVISORY}
\begin{itemize}[leftmargin=*, label=-]
    \item Chairman / Speedcargo Technologies Pte Ltd
\end{itemize}

% ---------------- Education ----------------
\section*{EDUCATION}
\textbf{PhD, Artificial Intelligence and Robotics} — Technical University of Munich (TUM), Germany \hfill {\color{muted}2012} \\
\textit{Grade: Magna Cum Laude \\
Advisor: Prof. Dr. Alois Knoll, Chair of Robotics and Artificial Intelligence,TUM, Germany \\
Reviewer: Prof. Dr. Dieter Fox, Former Global Head of Robotics (NVIDIA), Professor at University of Washington, Author of *Probabilistic Robotics*}

\textbf{Master of Science, Embedded Electronics and Computer Systems} — Tekniska Högskolan Jönköping, Sweden \hfill {\color{muted}2007} \\
\textit{Grade: Distinction \\ Master Thesis in Computer Vision at Philips Research Laboratories, The Netherlands}

\textbf{Bachelor of Engineering, Electronics and Telecommunications} — University of Pune, India \hfill {\color{muted}2004} \\
\textit{Grade: Distinction}


% ---------------- Skills ----------------
\section*{CORE COMPETENCIES}
\begin{multicols}{3}
\begin{itemize}[leftmargin=*]
    \item Startup Leadership
    \item High Performance Teams
    \item Fundraising \& Investor Relations
    \item AI / ML / Robotics Strategy
    \item Product Management
    \item Go-To-Market Strategy
    \item Enterprise Sales
    \item Fundraising and Board Matters
    \item ISO27001
\end{itemize}
\end{multicols}

% ---------------- Skills ----------------
\section*{TECHNICAL COMPETENCIES}
\begin{multicols}{3}
\begin{itemize}[leftmargin=*]
    \item Cloud Native Architectures
    \item \parbox[t]{\columnwidth}{C, C++, Go, Python, Java, JavaScript, Matlab, VHDL, SystemC}
    \item \parbox[t]{\columnwidth}{ Knowledge Graphs, Ontologies, Reasoning Engines, MongoDB, SQL}
    \item \parbox[t]{\columnwidth}{Docker, Ansible, Git, BitbucketPipelines}
    \item \parbox[t]{\columnwidth}{ROS, ZeroMQ, Google RPC, Thrift}
    \item \parbox[t]{\columnwidth}{Siemens ProfiNet, EtherCAT, Siemens Kineo, TCP/IP }
    \item \parbox[t]{\columnwidth}{Blender, ABB RobotStudio, Gazebo}
    \item Latex, Bash
    \item Linux, RTOS, Windows
    \item \parbox[t]{\columnwidth}{Zoho CRM, Jira, Confluence, MS Project}
\end{itemize}
\end{multicols}

% ---------------- Skills ----------------
\section*{LANGUAGES}
\begin{multicols}{3}
\begin{itemize}[leftmargin=*]
    \item {English - Full Profession Competency}
    \item {Malayalam - Mother Tongue}
    \item {Hindi - Proficient}
    \item {Marathi - Proficient}
    \item {German - Intermediate}
\end{itemize}
\end{multicols}

\section*{REFERENCES}
\begin{itemize}[leftmargin=*]
    \item {Available on request.}
\end{itemize}
\end{document}